
---
title: "Edgar Anderson’s Iris Data"
Date: 05-12-2022
output:
  pdf_document:
    toc: yes
    df_print: paged
  word_document:
    toc: yes
    df_print: paged
  html_document:
    toc: yes
    df_print: paged
    number_sections: no
    toc_float:
      collapsed: no
fontsize: 11pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

This famous ([Fisher's](https://en.wikipedia.org/wiki/Ronald_Fisher) or
[Anderson's](https://en.wikipedia.org/wiki/Edgar_Anderson)) iris data set gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are  *Iris setosa, versicolor, and virginica*.


# Usage

```{r usage, eval=FALSE}
iris
```


# Format

iris is a data frame with `r length(iris$Sepal.Length)` cases (rows) and `r length(iris)` variables (columns) named:

  * **Sepal.Length** 
  * **Sepal.Width** 
  * **Petal.Length** 
  * **Petal.Width** 
  * **Species** 
  

# Source

Anderson, Edgar (1935). "The irises of the Gaspe Peninsula." *Bulletin of the American Iris Society,* **59**: 2–5.\

Fisher, Ronald A. (1936). "The use of multiple measurements in taxonomic problems." *Annals of Eugenics,* **7** (Part **II**): 179–188.\


# Examples

We investigate the Sepal and Petal leaves for the three species in the Iris data:


```{r iris}
summary(iris)
```


To examine the Sepal leaves, we select the length and the width:


```{r sepal, echo=TRUE}
llen <- iris$Sepal.Length
lwid <- iris$Sepal.Width
```


Then we plot the data:


```{r sepal_plot, echo=TRUE}
plot(llen, lwid, xlab = "Length", ylab = "Width",
pch = 20, col = as.numeric(iris$Species))
legend("bottomright", legend = levels(iris$Species), col = 1:3, pch = 20)
```


We can also select the Petal leaves:

```{r petal, echo=TRUE}
llen <- iris$Petal.Length
lwid <- iris$Petal.Width
```


This gives us the following plot:

```{r petal_plot, echo=FALSE}
plot(llen, lwid, xlab = "Length", ylab = "Width",
pch = 20, col = as.numeric(iris$Species))
legend("bottomright", legend = levels(iris$Species), col = 1:3, pch = 20)
```






